Writing News Captions with Bags of Attention

### 2019-10-15 paper/paper.tex
Add word statistics to paper

\begin{table*}[t]
	\caption {Results on the NYTimes+ dataset}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
		\midrule
      Transformer & 17.2\% & 10.2\% & 6.55\% & 4.55\% & 19.1\% & 8.41\% & 40.4\% \\
      Transformer (location-aware) & 18.4\% & 11.2\% & 7.35\% & 5.16\% & 20.5\% & 9.21\% & 47.6\% \\
      \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Proper name metrics on the NYTimes+ dataset}
	\label{tab:results-names}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
		\midrule
      Transformer & 26.2\% & 31.5\% & 19.6\% & 29.3\% & 17.2\% & 21.3\%  \\
      Transformer (location-aware) & 30.1\% & 35.4\% & 23.6\% & 32.6\% & 22.1\% & 25.4\%   \\
		\bottomrule
	\end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
	\caption {Results on the NYTimes+ test set}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
		\midrule
      Transformer & 17.2\% & 10.2\% & 6.55\% & 4.55\% & 19.1\% & 8.41\% & 40.4\% \\
      Transformer (location-aware) & 18.4\% & 11.2\% & 7.35\% & 5.16\% & 20.5\% & 9.21\% & 47.6\% \\
      \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Proper name metrics on the NYTimes+ test set}
	\label{tab:results-names}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
		\midrule
      Transformer & 26.2\% & 31.5\% & 19.6\% & 29.3\% & 17.2\% & 21.3\%  \\
      Transformer (location-aware) & 30.1\% & 35.4\% & 23.6\% & 32.6\% & 22.1\% & 25.4\%   \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Word statistics on the NYTimes+ test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.4 & 17.1 \\
      Transformer  & 12.8 & 11.5 \\
      Transformer (location-aware) & 12.9 & 11.6  \\
		\bottomrule
	\end{tabular}
\end{table*}
